\newcommand{\tocitem}[4]{
	\item[#1] \textsc{#2} #3 \dotfill #4
}

\begin{center}
	{\LARGE\bfseries\MakeUppercase{sing-shü moh-loh.}}	\\[4ex]
	{\Large\MakeUppercase{gyiu iah shü.}}					\\
	% \vspace{1ex}
	\begin{multicols}{2}
		\columnseprule = 0.4pt
		\raggedcolumns
		{\textsc{Tön-sia} \hfill \textsc{Tsông-su}}		\\
		\begin{description}[noitemsep, labelwidth=6ex, topsep=1ex]
			\tocitem{Ts.}{Ts'iang-si}{kyi}{50}
			\tocitem{C.}{C'ih Yi-gyih}{kyi}{40}
			\tocitem{Lv.}{Li-vi}{kyi}{27}
			\tocitem{Ms.}{Ming-su}{kyi-liah}{36}
			\tocitem{Sm.}{Sing-ming}{kyi}{34}
			\tocitem{Is.}{Iah-shü-ô}{kyi}{24}
			\tocitem{Z.}{Z-s}{kyi}{21}
			\tocitem{Lt.}{Lu-teh}{kyi}{4}
			\tocitem{1 S.}{1 Sæh-meo-z}{kyi}{31}
			\tocitem{2 S.}{2 Sæh-meo-z}{kyi}{24}
			\tocitem{1 W.}{1 Lih-wông}{kyi-liah}{22}
			\tocitem{2 W.}{2 Lih-wông}{kyi-liah}{25}
			\tocitem{1 L.}{1 Lih-de}{ts-liah}{29}
			\tocitem{2 L.}{2 Lih-de}{ts-liah}{36}
			\tocitem{Yzl.}{Yi-z-læh}{kyi}{10}
			\tocitem{Nh.}{Nyi-hyi-mi}{kyi}{13}
			\tocitem{Yzt.}{Yi-z-t'ih}{kyi}{10}
			\tocitem{Ip.}{Iah-pah}{kyi}{42}
			\tocitem{S.}{S-p'in}{}{150}
			\tocitem{Tn.}{Tseng-nyin}{}{31}
		\end{description}
		\columnbreak
		{\textsc{Tön-sia} \hfill \textsc{Tsông-su}}		\\
		\begin{description}[noitemsep, labelwidth=6ex, topsep=1ex]
			\tocitem{Dj.}{Djün-dao}{}{12}
			\tocitem{Ko.}{Ngô-ko}{}{8}
			\tocitem{Y.}{Yi-se-ô}{shü}{66}
			\tocitem{Yl.}{Yia-li-mi}{shü}{66}
			\tocitem{E.}{Yia-li-mi}{e-ko}{5}
			\tocitem{Ys.}{Yi-si-kyih}{shü}{48}
			\tocitem{Dy.}{Dæn-yi-li}{shü}{12}
			\tocitem{'O.}{'O-si}{shü}{14}
			\tocitem{Iz.}{Iah-z}{shü}{3}
			\tocitem{Ô.}{Ô-mo-z}{shü}{9}
			\tocitem{Op.}{O-pô-ti}{shü}{1}
			\tocitem{In.}{Iah-nô}{shü}{4}
			\tocitem{Mi.}{Mi-kô}{shü}{7}
			\tocitem{No.}{Nô-ong}{shü}{3}
			\tocitem{Hp.}{Hah-pô-kôh}{shü}{3}
			\tocitem{Sf.}{Si-fæn-ngô}{shü}{3}
			\tocitem{Hk.}{Hah-kyi}{shü}{2}
			\tocitem{Sk.}{Sæh-kô-li-ô}{shü}{14}
			\tocitem{Ml.}{Mô-læh-kyi}{shü}{4}
		\end{description}
	\end{multicols}
	
	\vfill
	{\Large\MakeUppercase{sing iah shü.}}					\\
	% \vspace{1ex}
	\begin{multicols}{2}
		\columnseprule = 0.4pt
		\raggedcolumns
		{\textsc{Tön-sia} \hfill \textsc{Tsông-su}}		\\
		\begin{description}[noitemsep, labelwidth=6ex, topsep=1ex]
			\tocitem{Mt.}{Mô-t'a}{djün foh-ing shü}{28}
			\tocitem{Mk.}{Mô-k'o}{djün foh-ing shü}{16}
			\tocitem{Lk.}{Lu-kô}{djün foh-ing shü}{24}
			\tocitem{I'ö.}{Iah-ön}{djün foh-ing shü}{21}
			\tocitem{Sd.}{S-du}{'ang-djün}{28}
			\tocitem{Lm.}{Lo-mô}{shü-sing}{16}
			\tocitem{1 K.}{1 Ko-ling-to}{shü-sing}{16}
			\tocitem{2 K.}{2 Ko-ling-to}{shü-sing}{13}
			\tocitem{Kô.}{Kô-læh-t'a}{shü-sing}{6}
			\tocitem{Yf.}{Yi-feh-su}{shü-sing}{6}
			\tocitem{Fl.}{Fi-lih-pi}{shü-sing}{4}
			\tocitem{Kl.}{Ko-lo-si}{shü-sing}{4}
			\tocitem{1 T.}{1 T'ih-sæh-lo-nyi-kô}{shü-sing}{5}
			\tocitem{2 T.}{2 T'ih-sæh-lo-nyi-kô}{shü-sing}{3}
		\end{description}
		\columnbreak
		{\textsc{Tön-sia} \hfill \textsc{Tsông-su}}		\\
		\begin{description}[noitemsep, labelwidth=6ex, topsep=1ex]
			\tocitem{1 D.}{1 Di-mo-t'a}{shü-sing}{6}
			\tocitem{2 D.}{2 Di-mo-t'a}{shü-sing}{4}
			\tocitem{Dt.}{Di-to}{shü-sing}{3}
			\tocitem{Flm.}{Fi-li-meng}{shü-sing}{1}
			\tocitem{H.}{Hyi-pah-le}{shü-sing}{13}
			\tocitem{Nk.}{Ngô-kôh}{shü-sing}{5}
			\tocitem{1 P.}{1 Pi-teh}{shü-sing}{5}
			\tocitem{2 P.}{2 Pi-teh}{shü-sing}{3}
			\tocitem{1 I'ö}{1 Iah-'ön}{shü-sing}{5}
			\tocitem{2 I'ö}{2 Iah-'ön}{shü-sing}{1}
			\tocitem{3 I'ö}{3 Iah-'ön}{shü-sing}{1}
			\tocitem{Yd.}{Yiu-da}{shü-sing}{1}
			\item[Mz.] Iah-'ön-keh \textsc{Moh-z-loh} \dotfill 22
		\end{description}
	\end{multicols}
\end{center}